Bird beak's elaboration and innovation

### 2022-10-07 Analysis/03.1-Elaboration_innovation_analysis[statistics].Rmd
Update 03.1-Elaboration_innovation_analysis[statistics].Rmd

## Load the covar
load(file = "../Data/Processed/shapespace_passeriformes_5996t.MCMCglmm")
shapespace_passeriformes_posteriors <- shapespace_passeriformes[[1]]
rm(shapespace_passeriformes)
## Load the data for the passeriformes
load(file = "../Data/Processed/shapespace_passeriformes_two_levels.rda")
## Select the data
shapespace_passeriformes <- shapespace_passeriformes_two_levels[[1]]$space
## Clean garbage
rm(shapespace_passeriformes_two_levels)

@@

```{r, eval = TRUE, echo = FALSE}
load("../Data/Processed/ellipses_stats.rda")
source("../Functions/stats.utilities.R")

>>>>

## Load the covar
load(file = "../Data/Processed/shapespace_passeriformes.MCMCglmm")
shapespace_passeriformes_posteriors <- shapespace_passeriformes[[1]]
rm(shapespace_passeriformes)
## Load the data for the passeriformes
load(file = "../Data/Processed/shapespace_passeriformes_two_levels.rda")
## Select the data
shapespace_passeriformes <- shapespace_passeriformes_two_levels[[1]]$space
## Clean garbage
rm(shapespace_passeriformes_two_levels)

@@

```{r, eval = TRUE, echo = FALSE}
load("../Data/Processed/ellipses_stats.rda")
source("../Functions/stats.utilities.R")
library(xtable)
